---
title: "B Tables and Figures (1)"
description: |
  Code to create tables and figures from our paper.
author:
  - name: Rachael Burke
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
---

This (A) markdown shows the descriptive tables and figures, and the "base" plots of actual observed TB diagnoses.  We use this base plots in the "analysis" markdown to build up lines showing predictions [including showing our working as going along].

The final (post-analysis) tables and figs are drawn in "b_tableandfig.Rmd"

# Load data

```{r}
library(here)
library(tidyverse)
library(janitor)
library(lubridate)
library(arsenal) # for tableby

acf_start_date <- dmy("01 April 2011") 
acf_end_date <- dmy("30 Sep 2014")

# These are the "long" datasets (one row per person with TB)
tb_2009_2018 <- readRDS(file=here("data","tb_2009_2018.rds")) # Each row represents one adult in Blantyre City diagnosed with TB, information on method of TB diagnosis, quarter-year of diagnosis and whether they lived in an ACF or non-ACF area.
tb_2011_2018 <- readRDS(file=here("data","tb_2010_2018.rds")) # Each row represents one adult in Blantyre City diagnosed with TB, but with more information per person than the 2009_2010 file (i.e. includes HIV status, age and sex)
tb_2009_2010 <- readRDS(file=here("data","tb_2009_2010.rds"))
pop <- readRDS(file=here("data","pop.rds")) # Blantyre City adult population by quarter-year and ACF vs. non-ACF area

# These are the "wide" datasets with TB notifications grouped by quarter and with CNR
cnrs_smp_clinic <- readRDS(here("data","cnrs_smp_clinic.rds"))
cnrs_all <- readRDS(here("data","cnrs_all.rds"))  # all form
cnrs_d <- readRDS(here("data","cnrs_d.rds")) # cnrs by method of diagnosis
```

# Figure 1: Map

This is a map of Blantyre.  Using "tmap". Note that shape files are not included in this repo as they have been extremely "fussy" and I have struggled to get them working properly. 

```{r}
library(sf)
library(tmaptools)
library(tmap)
library(OpenStreetMap)


blantyre_city <- sf::st_read(here("data_raw","blantyre_tas.kml")) # rows 1-9 are Blantyre Rural TAs
acf <- blantyre_city[c(9,14:18),]
nonacf <- blantyre_city[c(10:13,19:31),]

clinic <- sf::st_read(here("data_raw","waypoints of facilities and landmarks.shp")) 
clinic <- clinic[c(1:11),]
osm <- read_osm(bb(blantyre_city[c(9:31),], current.projection="wgs84"), ext=1.1, raster=F)

tm_shape(osm) + 
  tm_rgb() +
  tm_shape(nonacf) +
  tm_fill(alpha=0.2, col="#46ACC8") +
  tm_borders(col="#46ACC8", alpha=0.8) +
  tm_shape(acf) +
  tm_fill(alpha=0.2, col="#B40F20") +
  tm_borders(col="#B40F20", alpha=0.8) +
  tm_shape(clinic) +
  tm_symbols(size=0.2, shape=15, col="black") +
  tm_scale_bar(color.dark = "black") +
  tm_compass(position=c("right","top")) +
  tm_add_legend(type="fill", col=c("#46ACC8","#B40F20"), labels=c("Non-ACF area","ACF area")) +
  tm_add_legend(type="symbol", col="black", shape=15, labels=c("Healthcare clinic")) +
  tm_legend(legend.position=c("left","bottom"))

```


# Table 1

Came from data in Dr M Nliwasa's work / PhD thesis.

# Figure 2

```{r}
cnrs_d <- cnrs_d %>% 
  mutate(acfarea_l = 
           case_when(acfarea=="b) ACF" ~ "ACF area", 
                     acfarea=="a) Non-ACF" ~ "Non-ACF area")) # this is so that the graph gets labelled properly / clearly

diagnosis_method <- ggplot(cnrs_d, aes(x=yq_mid + days(45), y=cnr, fill=diagnosed)) +
  #annotate(geom="rect", xmin=acf_start_date, xmax=acf_end_date, ymin=-Inf, ymax=Inf, alpha=0.4) +
  geom_area(alpha=0.6 , size=.5, colour="black", data=.%>% filter(acfarea=="b) ACF")) +
  geom_area(alpha=0.6 , size=.5, colour="black", data=.%>% filter(acfarea=="a) Non-ACF")) +
  geom_vline(xintercept=acf_start_date, linetype=2) +
  geom_vline(xintercept=acf_end_date, linetype=2) +
  facet_wrap(~acfarea_l) +
  labs(x="Year and quarter",
       y="Case notification rate",
       fill="Method of TB dx") +
  scale_fill_manual(values=c("#46ACC8","#E58601","#E2D200","#B40F20", "#68BB59")) +
  theme_bw()

diagnosis_method

ggsave(plot=diagnosis_method, file=here("figures","Fig2_CNR_by_diagnosis_method.pdf"), width=10, height=7)
```

# Fig 3 Base plot

This gets built up later with data from "analysis.rmd".  See b_tableandfig for final figure from paper.


```{r}
plot_fx <- function(df){
ggplot(df) +
  annotate(geom="rect", xmin=acf_start_date, xmax=acf_end_date, ymin=-Inf, ymax=Inf, alpha=0.1) +
  geom_point(aes(x=yq_mid, y=cnr, color=acfarea), shape=20, alpha=0.8) +
  geom_line(aes(y=cnr, x=yq_mid, color=acfarea), alpha=0.3) +
  labs(x="Time (quarter-year)",
       y = "Case notification rate (per 100,000 person-years)",
       color="Area \n(ACF vs. non-ACF)",
       caption="Shaded area is time ACF was ongoing") +
  scale_color_brewer(palette = "Set1") +
  theme_bw()
}

cnr_base_plot_all <- plot_fx(cnrs_all) +
  labs(title="All form TB")
cnr_base_plot_all

cnr_base_plot_micro_clinic <- plot_fx(cnrs_smp_clinic) +
  labs(title="Smr/Xpert positive TB")
cnr_base_plot_micro_clinic

save(cnr_base_plot_micro_clinic, file=here("data/cnr_base_plot_micro_clinic.rdata")) # save both the .rdata object so can re-draw and add
ggsave(plot=cnr_base_plot_micro_clinic, here("figures","cnr_base_plot_micro_clinic.pdf"), width=10, height=7) # and the pdf

save(cnr_base_plot_all, file=here("data/cnr_base_plot_all.rdata")) # save 
ggsave(plot=cnr_base_plot_all, file=here("figures","cnr_base_plot_all.pdf"), width=10, height=7)
```

# Numbers quoted in text

Numbers quoted in text.

```{r, message=F}
pop %>% filter(yq==dmy("01 Jan 2011"))
tb_2009_2018 %>% nrow()

tb_2009_2018 %>% tabyl(acf) %>% adorn_totals()
tb_2009_2018 %>% tabyl(diagnosed) %>% adorn_totals()

tb_2009_2018 %>% filter(diagnosed=="d) Smr clinic" | diagnosed=="c) Xpert clinic" | diagnosed=="e) Direct ACF") %>% nrow()
(tb_2009_2018 %>% filter(diagnosed=="d) Smr clinic" | diagnosed=="c) Xpert clinic" | diagnosed=="e) Direct ACF") %>% nrow()) / nrow(tb_2009_2018)

tb_2009_2018 %>% filter(diagnosed=="a) Clinically dx" | diagnosed=="b) Smr/cult TB lab") %>% nrow()
(tb_2009_2018 %>% filter(diagnosed=="a) Clinically dx" | diagnosed=="b) Smr/cult TB lab") %>% nrow()) / nrow(tb_2009_2018)

tb_2011_2018 %>% tabyl(sex) %>% adorn_totals()
tb_2011_2018 %>% tabyl(ageg) %>% adorn_totals()
summary((tb_2011_2018 %>% filter(sex=="Female"))$age)
summary((tb_2011_2018 %>% filter(sex=="Male"))$age)
tb_2011_2018 %>% tabyl(hiv) %>% adorn_totals()

pop %>% filter(yq==dmy("1 jan 2009"))
pop %>% filter(yq==dmy("1 oct 2018"))

cnrs_smp_clinic %>% 
  group_by(acfarea,acftime) %>%
  summarise(cnr=mean(cnr))

cnrs_all  %>% 
  group_by(acfarea,acftime) %>%
  summarise(cnr=mean(cnr))
```
```{r, message=F}
tb_2011_2018 %>% nrow()
tb_2011_2018 %>% tabyl(diagnosed)
7525 + 1816

# This is about how many of those who were initially "smear neg" when starting TB treatment were subsequently micro confirmed by culture (by ACF area and ACF time - during ACF vs. post ACF).
# My prefered 'tabyl' options (add totals, percentages)
rmb_tabyl <- function(df) {
 df %>% adorn_totals(where="col") %>% adorn_percentages(denominator="row") %>% adorn_pct_formatting(digits=2) %>% adorn_ns()
}

tb_2011_2018 %>% 
  filter(yq>=dmy("01 April 2011")  & yq<dmy("01 Oct 2014")) %>% 
  filter(diagnosed=="a) Clinically dx" | diagnosed=="b) Smr/cult TB lab") %>%
  mutate(diagnosed=as.character(diagnosed)) %>%
  tabyl(acfarea,diagnosed) %>% rmb_tabyl()

tb_2011_2018 %>% 
  filter(yq>=dmy("01 April 2011")  & yq<dmy("01 Oct 2014")) %>% 
  mutate(diagnosed=as.character(diagnosed)) %>%
  filter(diagnosed=="a) Clinically dx" | diagnosed=="b) Smr/cult TB lab") %>%
  tabyl(acfarea, diagnosed) %>% chisq.test(.,tabyl_results=T)
tb_2009_2018 %>% 
  filter(acfarea=="b) ACF") %>%
  filter(yq>=dmy("01 April 2011")) %>% 
  mutate(diagnosed=as.character(diagnosed)) %>%
  filter(diagnosed=="a) Clinically dx" | diagnosed=="b) Smr/cult TB lab") %>%
  tabyl(acftime,diagnosed) %>% rmb_tabyl()

tb_2009_2018 %>% 
  filter(acfarea=="b) ACF") %>%
  filter(yq>=dmy("01 April 2011")) %>% 
  mutate(diagnosed=as.character(diagnosed)) %>%
  mutate(acftime=as.character(acftime)) %>%
  filter(diagnosed=="a) Clinically dx" | diagnosed=="b) Smr/cult TB lab") %>%
  tabyl(acftime,diagnosed) %>% chisq.test()
```


# S. table

Supplementary table numbers (NB. for publication quality output I have re-done this in a dedicated markdown that I could knit to pdf, code here is to display the values in a less "polished" way).

```{r,asis=T}
mycontrols  <- tableby.control(test=FALSE)

# Table 1A is pre-ACF (data collected retrospectively)
labels(tb_2009_2010) <- c(diagnosed = "TB type")

Stab1A <- tableby(acf ~ diagnosed, data=tb_2009_2010, control=mycontrols)
summary(Stab1A, title="People with TB 2009-2011.Q1", text=T)

# Table 1B is ACF and post-ACF time (data collected prospectively)
tb_2011_2018b <- tb_2011_2018 %>% mutate(ageg=as.character(ageg)) # this is to get rid of "empty" 0-14 factor
labels(tb_2011_2018b)  <- c(ageg = 'Age (years)', sex = "Sex", diagnosed = "TB type", Facility = "Type of Facility", hiv="HIV Status", art = "ART status")
Stab1B <- tableby(acf ~ sex + diagnosed + facility + hiv + art + ageg, data=tb_2011_2018b, control=mycontrols)
summary(Stab1B, title="People with TB 2011.Q2-2018", text=T) 

Stab <- list(Stab1A, Stab1B)

#write2word(Stab, here("test2.docx"), title="Characteristics of people with TB")

```




